### 2021-06-09 letter/responseLetter.tex

\begin{document}

\begin{letter}{JSS Editors,}
\opening{The comments of the reviewers have been very useful. They made us aware that some important points we were trying to convey remained obscure. We have corrected infelicities of presentation and all errors that the reviewers brought to our attention. The text in {\color{blue}blue} indicates how we have dealt with each individual comment.}

{\bf Reviewer 1}

\begin{itemize}
\item In the first place, qhat I missed is an overview of the empirical studies conducted and the relation between 
first and second experiment. I would recommend to include, before Sections 3.2 and 3.3, a section 
presenting the overall research methodology and the connections between the studies - in this sense, 
a figure reporting the various steps would be appreciated; Figure 2 only summarizes the design of the first study.

@@

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item In the second place, I would recommend to include more details on the experiments conducted. This is especially 
true for the second study, where Section 3.3 is a bit shallow. The three steps of the methodology are indeed shortly 
described without providing enough details, hence possibly precluding verifiability and replicability. In addition, the 
methodology is not linked to the research questions: I would recommend to restructure Section 3 in order to have 
data extraction processes and data analysis producedures for each research question.

@@

\vspace{0.2cm}

{\color{blue}{\bf Answer:} We changed Section 3.3 to detail our approach better. We also created a picture that can help understand the methodology of our second study.}

@@

\vspace{0.2cm}

\item The proposed DroidXP benchmark seems not to be available, which is a pity since it might be very useful for other 
researchers. I believe the paper may have a stronger impact if the tool would be available. The same is true for the 
data and scripts used for the experiments. I would appreciate if the paper may have an online repository making all 
data and tools available.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} Thanks for this comment. Our tool actually is available at gitHub repository at:

https://github.com/droidxp/benchmark.
 \vspace{0.2cm}

We also provide data and scripts of our experiments on-line at:

https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html. 
\vspace{0.2cm}\newline
At Section 1 (Introduction) we highlight the existence of these 2 repositories that can be useful for other researchers interested in our study.}

@@

\vspace{0.2cm}

\item In Figure 2, you used ``Malicious'', but in most other places, you used ``Malign''. Please unify your choice of terminology.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} Thanks for this observation. We change the picture and unify our terminology.}

@@

\vspace{0.2cm}

\item In 3.3, you mentioned ``we investigate whether or not a more advanced static analysis approach is promising for mining 
Android sandboxes. To this end, we leverage the FlowDroid taint analysis algorithms...''. True, FlowDroid has its edge 
in privacy leakage detection, but what's your justification for saying FlowDroid is more advanced in terms of static analysis?

\vspace{0.2cm}

{\color{blue}{\bf Answer:} Thanks for raising this question. Here we were intended to say that FlowDroid implements a more advanced static analysis approach than DroidFax. We agree that the sentence is ambiguous, and we fixed that in the new version of the paper (first paragraph
  of section 3.3).}

@@

\vspace{0.2cm}

\item Typos:
1. Page 3: to explains -- to explain.
2. Page 3: BLL-Study study -- BLL-Study.
3. Page 8, does not computed -- does not compute.
4. Page 9, of our experimental -- of our experiments.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} Sorry about these typos and grammar. We corrected all of them. Thanks.}

@@

\vspace{0.2cm}

\item Introduction, para 3 is repeating para 2

\vspace{0.2cm}

{\color{blue}{\bf Answer:} Paragraphs 2 and 3 have indeed similar content. We removed paragraphs 3.}

@@

\vspace{0.2cm}

\item ``The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the
analysis must often assume that additional behaviors are possible than actually would be.''
Please explain

\vspace{0.2cm}

{\color{blue}{\bf Answer:} We explained better the sentence at Introduction, paragraph 3, where we add the follow text: ``Many times, codes are interpreted, decrypted, or even downloaded at runtime. In these cases, the static analysis could be ineffective for mining sandboxes, since if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.''}

@@

\vspace{0.2cm}

\item ``We presented and evaluated DroidXP in a conference paper [11]''
What is DroidXP? It should be introduced to a reader who is not familiar.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} We agree with that. To mitigate this issue, we introduced better DroidXP, contextualizing why its development was important for our study. Text improvement is present in the paragraph 6 of introduction}

@@

\vspace{0.2cm}

\item Google play - Google Play
* java - Java / android - Android
* ``Another approach to rooting''
What is rooting?

\vspace{0.2cm}

{\color{blue}{\bf Answer:} Sorry about these typos. We corrected all of them. Thank one more time. With respect to ``rooting'': It's a process performed on Android devices like smartphones or tablets, which allows users of the Android mobile operating system, to execute privileged commands that are typically unavailable at its default configuration. The term comes from the fact that Android system is based on Linux, and this system has a (superuser), called root, which has access to administrative permissions as on Linux.\newline
From: https://en.wikipedia.org/wiki/Rooting(Android)
}

@@

\vspace{0.2cm}

\item Please rephrase:
``Those are kind of attack that usually tackled with the Android Mining Sandbox''
``For instance, Whaley et al. [18] combine dynamic and static analysis for API mining and so extract interface from software components.''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} With respect to the first sentence, we decided to remove it, since we realized that it was misleading. The second sentence we rephrase like : ``For instance Whaley et al. [18] combine dynamic and static analysis for API mining and so infer program behavior based on an example use of a Java class.''}

@@

\vspace{0.2cm}

\item What are sensitive behaviors? ``showed that Droidbot is able to trigger an amount of sensitive behaviors''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} Sensitive behaviors at Android context occurs when  an Android application functionality can result in accessing or leaking of Android users sensitive data. Example of sensitive behaviors: File accesses and network access. We improve the text with this definition at Background and related works Section, paragraph 6.}

@@

\vspace{0.2cm}

\item Please rephrase:
``From the same authors, another test generator tool for Android, described as Humanoid [23], is a Droidbot evolution and
presents a proposal that can generate humans like tests inputs, using deep learning.''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} We rephrase the text at Background and related works Section, paragraph 6, to better explain Humanoid test generation tool.}

@@

\vspace{0.2cm}

\item Briefly explain the taint analysis
``Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} We agree that taint analysis explanation was very briefly. We reviewed our Background and related works Section, to better explain taint analysis from paragraph 7. We explained better the concept of ``source'' and ``sink'', and present how the analysis identifies sensitive information leakage, detecting taint flow between “source” and “sink”. To improve understanding, we also present a simple Listing (Listing 1), that present a simple data leakage example through data flows within source code Java. }

@@

\vspace{0.2cm}

\item Please explain:
``FastDroid [28] mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} To address this issue, we explained better how FastDroid improves the taint analysis efficiency at the last paragraph of Background and related works Section}

@@

\vspace{0.2cm}

\item Section 3.1, the help text is not adding much value

\vspace{0.2cm}

{\color{blue}{\bf Answer:} Thanks for raising this point. The section 3.1 presented our Benchmark tool DroidXP. We understand that the tool description was important for the paper since it was helpful for our first study conduction. DroidXP helped us to easily integrate the different test generation tools, and understand the effect of the static analysis component at each integrated tool. It was useful for us and can be very useful for other researchers. We
reviewed the first paragraph of section 3.1 to clarify the importance of DroidXP for our study conduction.}

@@

\vspace{0.2cm}

\item Please rephrase: ``After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} We agree that the sentence was messy. We rephrased the sentence to clarify the first paragraph of Section 4.1. ``Then we repeated the process, however this time we isolate the effect of the static analysis component of DroidFax.''}

### 2021-06-09 letter/responseLetter.tex

\vspace{0.2cm}

\item Typos:
1. Page 3: to explains -- to explain.
2. Page 3: BLL-Study study -- BLL-Study.
3. Page 8, does not computed -- does not compute.
4. Page 9, of our experimental -- of our experiments.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Sorry about these typos and grammar. We corrected all of them. Thanks.}

@@

\vspace{0.2cm}

\item Introduction, para 3 is repeating para 2

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Paragraphs 2 and 3 have indeed similar content. We removed paragraphs 3.}

@@

\vspace{0.2cm}

\item ``The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the
analysis must often assume that additional behaviors are possible than actually would be.''
Please explain

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We explained better the sentence at Introduction, paragraph 3, where we add the follow text: ``Many times, codes are interpreted, decrypted, or even downloaded at runtime. In these cases, the static analysis could be ineffective for mining sandboxes, since if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.''}

@@

\vspace{0.2cm}

\item Please rephrase:
``Those are kind of attack that usually tackled with the Android Mining Sandbox''
``For instance, Whaley et al. [18] combine dynamic and static analysis for API mining and so extract interface from software components.''

\vspace{0.2cm}

{\color{blue}{\bf Answer.} With respect to the first sentence, we decided to remove it, since we realized that it was misleading. The second sentence we rephrase like : ``For instance Whaley et al. [18] combine dynamic and static analysis for API mining and so infer program behavior based on an example use of a Java class.''}

@@

\vspace{0.2cm}

\item What are sensitive behaviors? ``showed that Droidbot is able to trigger an amount of sensitive behaviors''

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Sensitive behaviors at Android context occurs when  an Android application functionality can result in accessing or leaking of Android users sensitive data. Example of sensitive behaviors: File accesses and network access. We improve the text with this definition at Background and related works Section, paragraph 6.}

@@

\vspace{0.2cm}

\item Please rephrase:
``From the same authors, another test generator tool for Android, described as Humanoid [23], is a Droidbot evolution and
presents a proposal that can generate humans like tests inputs, using deep learning.''

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We rephrase the text at Background and related works Section, paragraph 6, to better explain Humanoid test generation tool.}

@@

\vspace{0.2cm}

\item Briefly explain the taint analysis
``Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs''

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We agree that taint analysis explanation was very briefly. We reviewed our Background and related works Section, to better explain taint analysis from paragraph 7. We explained better the concept of ``source'' and ``sink'', and present how the analysis identifies sensitive information leakage, detecting taint flow between “source” and “sink”. To improve understanding, we also present a simple Listing (Listing 1), that present a simple data leakage example through data flows within source code Java. }

@@

\vspace{0.2cm}

\item Please explain:
``FastDroid [28] mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.''

\vspace{0.2cm}

{\color{blue}{\bf Answer.} To address this issue, we explained better how FastDroid improves the taint analysis efficiency at the last paragraph of Background and related works Section}

@@

\vspace{0.2cm}

\item Please rephrase: ``After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm''

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We agree that the sentence was messy. We rephrased the sentence to clarify the first paragraph of Section 4.1. ``Then we repeated the process, however this time we isolate the effect of the static analysis component of DroidFax.''}

### 2021-06-09 background.tex
update on the response letter to address some observation from R3

Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code~\cite{DBLP:journals/corr/abs-2002-04540}
%\kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}
, calling Java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls. Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access. Those are kind of attack that usually tackled with the Android Mining Sandbox \cite{DBLP:conf/icse/JamrozikSZ16}.

@@

Automatically mining software resources or components, to infer behavior is not new, and has been discussed before. For instance, Whaley et al.~\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so extract interface from software components. Ammons et al~\cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning
approach, called specification mining, to discover temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.

%\kn{Please write one sentence here saying why test generation tools could solve the problem, and then list the related work. The term test generation comes out out nowhere.} 
The main purpose of test generation tool is to find bugs. However, it also can be used to explore program behavior, and thus assist in the task of building Sandboxes. Regarding test generating tools used for mining Sandboxes, Jamrozik et al ~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps. Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy. In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors, like data leaks and file accesses, higher than Monkey. From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.

@@

Android applications contain within themselves the risk that sensitive data, such as credit card details, device information can be leaked into public sinks like the internet. Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs~\cite{boddenesec}. Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the Android operating system. Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves on precision of traditional approaches by including context and flow sensitivity. A significant issue with taint analysis is the cost of the tool itself hampering the performance. FastDroid~\cite{ZHANG2021102161} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.

%Although our study does not incorporate any taint analysis, one can imagine that applying taint analysis as an extra static analysis can drastically improve the precision of the dynamic analysis tools.

>>>>

Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code~\cite{DBLP:journals/corr/abs-2002-04540}
%\kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}
, calling Java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls. Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access.

@@

Automatically mining software resources or components, to infer behavior is not new, and has been discussed before. For instance, Whaley et al.~\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so infer program behavior based on an example use of a Java class. Ammons et al~\cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning
approach, called specification mining, to discover temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.

%\kn{Please write one sentence here saying why test generation tools could solve the problem, and then list the related work. The term test generation comes out out nowhere.} 
The main purpose of test generation tool is to find bugs. However, it also can be used to explore program behavior, and thus assist in the task of building Sandboxes. Regarding test generating tools used for mining Sandboxes, Jamrozik et al ~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random graphical user interface (GUI) exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps. Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy. In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors higher than Monkey. Sensitive behaviors at Android context occurs when an Android app functionality can result in accessing or leaking of Android users sensitive data. Example of sensitive behaviors are file accesses and network access. Another test generator tool for Android is called Humanoid \cite{DBLP:conf/kbse/LiY0C19}, which is a Droidbot evolution. It's also a GUI test generation that learning how humans interact with Android apps. In contrary to random input generators, Humanoid use the learned model to generate human-like test inputs, and prioritize the possible interactions on a GUI, according their importance.

@@

\textbf{Taint analysis} is a special type of static or dynamic analysis that purpose is to track data flows within programs~\cite{DBLP:conf/sigsoft/PauckBW18}. It can identify sensitive information leakage detecting taint flow between ``source'' and ``sink''. In Android apps context, a data leak occurs when sensitive data, such as contact, or device ID, flows from a private source to public sinks, like the internet. Taint analysis can present possible malicious data flow to malware detection tools or even for a human check, that can decide if the ``source-sink" relationship is or is not an unwanted behavior. Thereby, taint analysis monitors sensitive source ``tainted" through the app by starting at a pre-defined point.

In Android context, sources are the APIs in which apps access sensitive information, called sensitive APIs. The analysis follows the data flow until it reaches a sink, like a method that sends SMS. Finally, it brings exact information about which data will be leaked and where~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}. The Android SDK provides APIs that allow apps to send private data to other apps on the same device, or remote devices. As these APIs may lead to sensitive data leakage, they are security-critical and require special attention and control~\cite{DBLP:conf/osdi/EnckGCCJMS10}. (Listing~\ref{lst:sourceSink}) presents a simple data leakage example. In this example, the device information is captured at line 4 (source) and then leaked at line 9 (sink), by SMS transmission.

\begin{lstlisting}[caption={Simple Data Leakage},
      language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,
      label={lst:sourceSink}]

1 > localObject2 = (TelephonyManager)getSystemService("phone");
2 > if (localObject2 != null)
3 > {
4 >  this.imei = ((TelephonyManager)localObject2).getDeviceId();//source
5 > }
6 > if ("".equals(this.destMobile)) {
7 >  getDestMobile();
8 > }
9 > sendSMS(this.destMobile, "imei:" + this.imei)//sink
\end{lstlisting}

Wei et al.~\cite{DBLP:conf/issta/HuangDMD15} propose a scalable taint analysis for Android apps that applies traditional taint analysis techniques with targeted optimizations specific to Android OS. Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves on precision of traditional approaches by including context and flow sensitivity. A significant issue with taint analysis is the cost of the tool itself hampering the performance. FastDroid~\cite{DBLP:journals/compsec/ZhangTD21} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis, called taint value graph (TVG). To improve the efficiency and precision, FastDroid focuses on exploring the propagation of taint values, rather than the traditional data flow analysis. FastDroid constructs taint value graphs (TVGs) exploring taint values, then it extracts a subset of potential taint flows (PTFs) from it. FastDroid improves the analysis process by performing analysis only on (PTFs).

### 2021-06-09 introduction.tex
update on the response letter to address some observation from R3

Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often
assume that additional behaviors are possible than actually would be.
%\kn{Ok. In the first paragraph we discuss static analysis in general to detect vulnerabilities and now without mentioning it prior we seem to mention static analysis can also mine sandboxes. The overall flow of definitions needs some thought}
Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime. In addition,
code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features}
of programming languages are often used to introduce malicious behavior. Even though these claims
seem reasonable, previous research do not present empirical assessments about the limitations of static analysis to mine sandboxes.
Consequently, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.

@@

We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
and here we discuss the results of a broader investigation
that also uses DroidXP to explain the performance of static and dynamic analysis
approaches for mining sandboxes. Altogether, this paper brings the following contributions:

@@

\item A replication package of our study that is available on-line, including
  scripts for statistic analysis \footnote{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}
  and a benchmark for reproducing and extending our study.\footnote{https://github.com/droidxp/benchmark} 
\end{itemize}

>>>>

Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often
assume that additional behaviors are possible than actually would be. Many times, codes are interpreted, decrypted, or even downloaded at runtime. In these cases, the static analysis could be ineffective for mining sandboxes, since if static analysis determines that some behavior will not occur, it no longer will be checked at runtime. In addition, code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features} of programming languages are often used to introduce malicious behavior. Even though these claims seem reasonable, previous research do not present empirical assessments about the limitations of static analysis to mine sandboxes. Consequently, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.

@@

Along with the research advancements in the area of test case generation, new solutions are constantly emerging, and researchers and practitioners (including ourselves) have come up against technical difficulties in to reproduce the previous studies that compare test case generation tools to mine sandboxes. At our first study, to replicate \blls, we benefit from our benchmark tool, called DroidXP, developed to help researchers and practitioners to integrate test case generation tools and compare
their performance on mining sandboxes at Android platform. The repository for DroidXP is available at GitHub\footnote{https://github.com/droidxp/benchmark} and offers direct access to all source code, installation process, how to run and dependencies. We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20}, and here we discuss the results of a broader investigation that also uses DroidXP to explain the performance of static and dynamic analysis
approaches for mining sandboxes. Altogether, this paper brings the following contributions:

@@

\item A replication package of our study that is available on-line, including
  scripts for statistic analysis \footnote{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}
  and a benchmark for reproducing and extending our study.
\end{itemize}

### 2021-06-09 results.tex
update on the response letter to address some observation from R3

Our first study is a replication of the \blls.
As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default
configuration. After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm.
In this way, we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
Table~\ref{tab:fs} summarizes the results of the executions. The columns Exec. (WS) and Exec. (WOS) 
show the number of malwares identified when executing each tool with the
support of the DroidFax static analysis algorithms (WS) and without the support
of DroidFax static analysis algorithms (WOS). 
The Impact column shows 
(in percentage) to what extent the DroidFax static analysis algorithms influences
the performance of the sandboxes created after
executing the test generation tools. We calculate the impact
using Eq. (1).

@@

First we find that static analysis summaries had impact in the \blls. It was responsible for improving the results of the tools, between $16.44\%$ and $51.79\%$, discarding our Joker tool, answering our first research question (RQ1). Second, Table \ref{tab:fs} also summarizes our findings addressing the second research question (RQ2). We realized that disregarding the static analysis algorithms, and discarding Joker tool, among the tools analyzed in your study, Humanoid had the biggest performance drop, obtaining an effective performance of $28.12\%$, 27 malicious apps, among 96. The least affected was DroidBot, proving be the tool with better effective performance, in terms of the number of detected malware, obtaining an effective performance of $63.54\%$, 61 malicious apps, among 96 . Finally, we answered our last research question (RQ3) when we leverage sandboxes, complementing the dynamic analysis provided by test generation tool with tainted analysis algorithms. Our experiment highlight that $69.79\%$-$82.29\%$ of malware in dataset can be now uncovered by the complement of tainted analysis algorithms, evidencing that 
sandboxes can be further boosted when coupled with new static analysis techniques. We found that the number of identified malicious apps detected is increased for all cases, achieving at the best case, $82.29\%$ with DroidBot, a better performance than all five tools explored at \blls, even when they constructed a sandbox by combining all test generation tools at theirs work $75.49\%$. Table \ref{tab:tanted} display the increase of all tools explored at our research.

@@

\end{tabular} 
\caption{Malwares detected in 96 pair (B/M) increased by Tainted analysis Algorithms}
\label{tab:tanted}
\end{table}

>>>>

Our first study is a replication of the \blls.
As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default
configuration. Then we repeated the process, however this time we isolate the effect of the static analysis component of DroidFax. In this way, we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
Table~\ref{tab:fs} summarizes the results of the executions. The columns Exec. (WS) and Exec. (WOS) 
show the number of malwares identified when executing each tool with the
support of the DroidFax static analysis algorithms (WS) and without the support
of DroidFax static analysis algorithms (WOS). 
The Impact column shows 
(in percentage) to what extent the DroidFax static analysis algorithms influences
the performance of the sandboxes created after
executing the test generation tools. We calculate the impact
using Eq. (1).

@@

Our research reinforces the importance of exploring, the contributions of each component used in surveys. The \blls suggested a precision of almost $70\%$ of dynamic analysis tools to differentiate between  the benign and malicious app. However, when our work went into the details of the methodology adopted by \blls, it discovered that in their research, the authors ignore the fact that DroidFax tool statically analyzes the Android apps. Thereby, our research isolates the contribution of each analysis component (static and dynamic), and reveals that in the best case, dynamic analysis tools obtained a performance of $63.54\%$, showing an overestimation of the performance of the dynamic analysis tools for mining sandboxes at \blls.

Besides that, we also found that static analysis, performed by taint analysis algorithms, detected $60,42\%$ malware analyzed.  That fact made evident that it is possible to leverage sandboxes, complementing dynamic analysis tools with taint analysis algorithms. Researchers and apps developers could investigate the use of new static analysis techniques, or a combination of different approaches, to help developers on the task of developing safer apps.

Our results show that static analysis in short had an impact on the \blls and were responsible for improving the results of the tools, between $16.44\%$ and $51.79\%$, which answers our first research question (RQ1). Table \ref{tab:fs} also summarizes our findings addressing the second research question (RQ2). We realized that disregarding the static analysis algorithms, Humanoid had the biggest performance drop, obtaining an effective performance of $28.12\%$. The least affected tool was DroidBot, proving to be the tool with better effective performance in terms of the number of detected malware, obtaining an effective performance of $63.54\%$. Finally, we answered our last research question (RQ3) when we leverage the sandbox, complementing the dynamic analysis with taint analysis algorithms, showing that $69.79\%$-$82.29\%$ of malware can be now uncovered by the static analysis  complement. As a result, the number of malicious apps detected increased in all cases, achieving in the best case, $82.29\%$ with DroidBot , evidencing that a sandbox can be further boosted when coupled with new static analysis techniques. Dynamic analysis coupled with taint analysis algorithms showed a better performance than all five tools explored at \blls, even when they constructed a sandbox by combining all test generation tools when they achieved $75.49\%$ of malware detection. Table \ref{tab:tanted} displays an increase of malware detection on all tools explored in our research.

@@

\end{tabular} 
\caption{Malwares detected in 96 pair (B/M) increased by Taint analysis Algorithms}
\label{tab:tanted}
\end{table}
